---
title: "Group_8_RMCS2"

Yves HERI
Donald YOMBI
Geraldine BANDA
Bonaventure KAGARURA
Ferguson CHALUMBA
Athanase HAFASHIMANA
---

## Importing LIBRARIES
```{r}
library(plotly)
library(graphics)
library(biwavelet)
library(zoo)
library(xtable)
library(forecast)
library(TSA)

```

## Data Preprocessing 

```{r}
Cape_Town 	<- read.csv("Cape_Town_2_Group8.csv")
Data	<-  Cape_Town[,c(1,5)]
head(Data)
```
##############
### TASK 3 ###
##############


# Question 1 : Time series Plot of Precipitation and Temperature

# Precipitation
```{r}
Pre <- ts(Data$PRED, start = c(1960,1), end = c(2010,12), frequency = 12)
Temp <- ts(Data$TMPD, start = c(1960,1), end = c(2010,12), frequency = 12)
plot(Pre, ylab = 'Precipitation', main = 'Time Series of Precipitation', col='black')
lines(lowess(Pre,f=1/1),col='red')
```
# Save the plot
```{r}
png('Pre.png')
plot(Pre, ylab = 'Precipitation', main = 'Time Series of Precipitation', col='black')
lines(lowess(Pre,f=1/1),col='red')
dev.off()
```

# Temperature
```{r}
plot(Temp, ylab = 'Temperature', main = 'Time Series of Temperature', col='black')
lines(lowess(Temp,f=1/1),col="red")
```
# Save the plot
```{r}
png('Temp.png')
plot(Temp, ylab = 'Temperature', main = 'Time Series of Temperature', col='black')
lines(lowess(Temp,f=1/1),col="red")
dev.off()
```

### Question 2 ###

# De-trend the data
```{r}
PreD <- diff(Pre, differences = 1)
TempD <- diff(Temp, differences = 1)
PreD <- ts(PreD, start = c(1960,1), end = c(2010,12), frequency = 12)
TempD <- ts(TempD , start = c(1960,1), end = c(2010,12), frequency = 12)
```

# Plot the de-trended data : Precipitation
```{r}
plot(PreD, ylab = 'Precipitation', main = 'Detrended Time Series  of Precipitation', col='black')
lines(lowess(PreD,f=1/1),col="red")
```
# Save the plot
```{r}
png('Pre_Detrend.png')
plot(PreD, ylab = 'Precipitation', main = 'Detrended Time Series  of Precipitation', col='black')
lines(lowess(PreD,f=1/1),col="red")
dev.off()
```

# Plot the de-trended data : Temperature
```{r}
plot(TempD, ylab = 'Temperature', main = 'Detrended Time Series of Temperature', col='black')
lines(lowess(TempD,f=1/1),col="red")
```
# Save the plot
```{r}
png('Temp_Detrend.png')
plot(TempD, ylab = 'Temperature', main = 'Detrended Time Series  of Temperature', col='black')
lines(lowess(PreD,f=1/1),col="red")
dev.off()
```
### Question 3 ####
# Correlogram for Precipitation
```{r}
forecast::Acf(Pre, lag.max = 36, main = "Autocorrelation  for Precipitation ")
```

# Save the plot
```{r}
png('AutoCorr_Pre.png')
forecast::Acf(Pre, lag.max = 36, main = "Autocorrelation  for Precipitation ")
dev.off()
```

# Correlogram for Temperature
```{r}
forecast::Acf(Temp, lag.max = 36, main = "Autocorrelation  for Temperature")
```
# Save the plot
```{r}
png('AutoCorr_Temp.png')
forecast::Acf(Temp, lag.max = 36, main = "Autocorrelation  for Temperature")
dev.off()
```

```{r}
forecast::Acf(PreD, lag.max = 36, main = "Autocorrelation  for Detrended Precipitation Series")
```


```{r}
forecast::Acf(TempD, lag.max = 36, main = "Autocorrelation  for Detrended Temperature Series")
```
# Question 4 : Cross-correlation between Precipitation and Temperature

```{r}
forecast::Ccf(Pre,Temp)
```
# Save the plot
```{r}
png('Cross_corr.png')
forecast::Ccf(Pre,Temp)
dev.off()
```
##############
### TASK 4 ###
##############


## Question 1 : Find the periodogram

```{r}
png('periodogram.png')
par(mfcol = c(1,2))
p1 <- periodogram(Pre)
p <- periodogram(Temp)
dev.off()
```

## converting the frequency to periods
```{r}
png('frequency_gram.png')
period_Temp <- 1/p$freq
period_Prep <- 1/p1$freq
par(mfcol = c(1,2))
plot(period_Temp, p$spec, type = 'b', xlim = c(2,13), xlab = 'period', ylab = 'periodogram',
     main = 'Temperature')

plot(period_Prep, p1$spec, type = 'b', xlim = c(2,13), xlab = 'period', ylab = 'periodogram',
     main = 'Precipitation')
dev.off()
```
# Getting the 6-Moving average 
```{r}
Average <- rollmean(Pre, k = 6)
p <- periodogram(Average)
period_Prep <- 1/p$freq
plot(period_Prep, p$spec, type = 'b', xlim = c(2,13), xlab = 'Period', ylab = 'Periodogram', main = '6-Moving Average Precipitation')
```
# Save the plot
```{r}
png('Average_plot.png')
plot(period_Prep, p$spec, type = 'b', xlim = c(2,13), xlab = 'Period', ylab = 'Periodogram', main = '6-Moving Average Precipitation')
dev.off()
```
### Question 2 : 
```{r}
## Wavelet
   

#par(oma=c(0, 0, 0, 1), mar=c(5, 4, 4, 5) + 0.1)
yy=plot(wavelet1,  plot.cb = TRUE,lwd.coi = 1,col.coi="white",alpha.coi=0.5,col.sig="black",
        lwd.sig = 2, ncol = 768, tol = 0.95, plot.phase=F,ylab="Period(Year)", xlab = "Time(Year)",
        main='Temperature')
dev.off()


# wavelet coherence calculation
wcoh=wtc(cbind(timelong,Pre),cbind(timelong,Temp),dj=0.1,mother="morlet",max.scale=16) 

## plot of wavelet coherence
png('wavelet_coherence.png')
par(mfcol = c(1,1))
par(oma=c(0, 0, 0, 1), mar=c(5, 4, 4, 5) + 0.1) #To allow for colour bar to be included
plot(wcoh,  plot.cb = TRUE,lwd.coi = 1,col.coi="white",alpha.coi=0.5,col.sig="black",
     lwd.sig = 2, ncol = 768, tol = 0.95, plot.phase=T,ylab="Period(Year)", xlab = "Time(Year)",
     main='Wavelet Coherence') #plotting
dev.off()
```
